<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2015-04-29 competitions/competitions.Rmd
ENH:  More comp. stuff.

## <span style="color:green;">Klein 2009</span> <small>brain image registration</small>

@@

* 14 algorithms
* publicly available data
* unbiased evaluation

## <span style="color:green;">Klein 2009</span> <small>results</small>

@@

## <span style="color:green;">EMPIRE 2010</span> <small>lung image registration</small>

## <span style="color:green;">Multi-Atlas Label Challenge 2012</span> <small>atlas label fusion</small>

## <span style="color:green;">SATA Challenge 2012</span> <small>multi-modal/multi application label fusion</small>

## <span style="color:green;">BRATS 2013</span> <small>brain tumor segmentation</small>

@@

## <span style="color:green;">STACOM 2014</span> <small>cardiac motion estimation</small>

>>>>

## <span style="color:green;">Klein 2009</span>

@@

* 14 algorithms
* publicly available data
* different labeling protocols
* developers tune their own algorithms

## <span style="color:green;">Results</span>

@@

## <span style="color:green;">EMPIRE 2010</span>

![](./competitions/figures/EMPIRE10criteria.png)

* Alignment of lung boundaries,
* major fissures,
* annotated landmark pairs, and
* topology of displacement field.

## <span style="color:green;"> Results</span>

![](./competitions/figures/EMPIRE10Results.png)

## <span style="color:green;">Multi-Atlas 2012</span>

![](./competitions/figures/NKI30_MALF.png)

## <span style="color:green;">Results</span>

![](./competitions/figures/MALF2012.png)

## <span style="color:green;">SATA 2013</span>

## <span style="color:green;">BRATS 2013</span>

@@

## <span style="color:green;">STACOM 2014</span>
